\documentclass{book}
\usepackage[hidelinks]{hyperref}
\usepackage{amsthm}
\usepackage{listings}

\theoremstyle{definition}
\newtheorem*{examp}{Ex}
\newtheorem{quest}{Q}
\newtheorem*{theo}{Theorem}
\newtheorem*{alg}{Algorithm}
\newtheorem*{prf}{Proof}

\title{In-class Graph Question}
\author{Ashana Dhaliwal, Bushra Awan, Tariq ..., Chris Wozniak}

\begin{document}
\maketitle
\section*{In-class Questions}
	\begin{quest}
		Provide an example of a consistent graph, including an ambiguous pair.
		\begin{examp}
			A set of 4 nodes, 3 of them similar, and one being different. Here the graph is not complete, meaning there
			are ambiguous values present.
			\begin{equation}
			(1, 2, 1), 
			(1, 3, 1),
			(3, 4, 0)
			\end{equation}
		\end{examp}
		This graph would be consistant as the ambiguous pairs cannot determine similarities, but we do have a clear 
		difference between node 4 and 3. Since 3 is similar to the rest of the nodes, we can draw the conclusion through
		transitivity that the rest of the nodes will be different to 4.
	\end{quest}
	\begin{quest}
		Provide an inconsistant graph, with an ambiguous pair.
		\begin{examp}
			Another set of 4 nodes, where we have 4 connections out of a total of 6 possible.
			\begin{equation}
			(1, 2, 1), 
			(1, 3, 1),
			(3, 4, 1),
			(2, 4, 0)
			\end{equation}
		\end{examp}
		Here the graph shows a path to all 4 nodes, where each edge is weighted \textit{similar}, however there also
		exists a path between 2 and 4 which is weighted \textit{different}. This shows that we have an inconsistancy,
		since nodes 2, and 4 are both similar \textbf{and} different.
	\end{quest}
	\begin{quest}
		How can this problem be stated as a graph problem?
		\begin{examp}
			Our solution is to create a weighted, undirected graph $G$, where each edge $e=(i,j,k)$, $i,j \in V$, $e \in E$
			and $k \in \{0,1\}$ having 1 represent similar, and 0 being different. \textbf{Ambiguous} pairs are simply left 
			out of the graph.
		\end{examp}
	\end{quest}
	\begin{quest}
		Completed, as above.
	\end{quest}
	\begin{quest}
		Which algorithm: DFS, BFS, or Top. Sort could be modified/used to solve this problem?
		\begin{examp}
			A Breadth-First search algorithm could be used to solve this problem easily. We simply denote the first node
			as a group, say $A$, to start. Then we traverse each edge of the nodes neighbors, assigning them to a group
			based on the edge weight (A if similar, B if different).\\

			IF we encounter a situation where two nodes are connected, but the edge says they should be similar/different
			when they arent/are respectively we have found an inconsistancy, and the graph can be returned inconsistant.
		\end{examp}
	\end{quest}
\newpage
	\section*{The Algorithm:}
\begin{lstlisting}
set node a to group A
add a to the queue
for each node n in the queue
	for each neighbor i of node n
		if i's group is null
			assign i to appropiate group
			add i to queue.
		else if i's group is inconsistant with n's group and edge
			return inconsistant
return consistant.
\end{lstlisting}
	\section*{Asymptotic Analysis}




\end{document}